---
title: "Longitudinal Identity Network Paper Results"
output: html_notebook
---

# Import and Prepare

```{r, echo=FALSE, include=FALSE}
library(groundhog)
pkgs <-  c("tidyverse","here", "lmerTest", "sjPlot","broom.mixed", "kableExtra", "ggeffects", "gt", "brms", "bayestestR","ggdist","tm","wordcloud")
groundhog.day <- '2022-07-25'
groundhog.library(pkgs, groundhog.day)
here::i_am("Analyses/idNetPrelimAnalyses.Rmd")
```

```{r, include=FALSE}
fullLong <- read.csv(here("Data/longIdentityNet.csv"))
fullShort <- read.csv(here("Data/shortIdentityNet.csv"))
fullLong$subID <- as.numeric(fullLong$subID)
fullData <- fullLong %>% full_join(fullShort, by = c("subID","Time"))

indDiffs <- fullData[!duplicated(fullData$subID),]
```

```{r,include=FALSE}
scaled <- apply(fullData[6:ncol(fullData)], 2, function(x) scale(x))
colnames(scaled) <- paste0(colnames(scaled),".Z")
fullData <- cbind(fullData, scaled)


scaled <- apply(fullShort[2:ncol(fullShort)], 2, function(x) scale(x))
colnames(scaled) <- paste0(colnames(scaled),".Z")
fullShort <- cbind(fullShort, scaled)

fullShort <- fullLong %>% distinct(subID, Time, Stability, totPropAdded, totPropDropped) %>% right_join(fullShort, by=c("subID","Time"))

fullData <- fullData %>% mutate_at(c("Salient", "I", "M", "I", "P", "St", "Ent", "Sim", "Proto", "A", "D", "MemUnc", "IdUnc", "Should", "Consist", "Salient", "Ideal", "BExp", "GExp", "BelPer"), ordered)
```

```{r, include=FALSE}
ncores = parallel::detectCores()
options(mc.cores = parallel::detectCores())
```

```{r, include=FALSE}
named.contr.sum<-function(x, ...) {
    if (is.factor(x)) {
        x <- levels(x)
    } else if (is.numeric(x) & length(x)==1L) {
        stop("cannot create names with integer value. Pass factor levels")
    }
    x<-contr.sum(x, ...)
    colnames(x) <- apply(x,2,function(x) 
         paste(names(x[x>0]), names(x[x<0]), sep="-")
    )
    x
}
fullData$Categ <- as.factor(fullData$Categ)
contrasts(fullData$Categ) <- named.contr.sum(levels(fullData$Categ))
devtools::source_url("https://raw.githubusercontent.com/JacobElder/MiscellaneousR/master/corToOne.R")
devtools::source_url("https://raw.githubusercontent.com/JacobElder/MiscellaneousR/master/plotCommAxes.R")
devtools::source_url("https://raw.githubusercontent.com/JacobElder/MiscellaneousR/master/named.effects.ref.R")
```

# Wordcloud

```{r}
#Create a vector containing only the text
text <- as.vector(fullData$identity)
# Create a corpus  
docs <- Corpus(VectorSource(text))
docs <- docs %>%
  tm_map(removeNumbers) %>%
  tm_map(removePunctuation) %>%
  tm_map(stripWhitespace)
docs <- tm_map(docs, content_transformer(tolower))
docs <- tm_map(docs, removeWords, stopwords("english"))
docs <- tm_map(docs, removeWords, c("the","and"))

dtm <- TermDocumentMatrix(docs) 
matrix <- as.matrix(dtm) 
words <- sort(rowSums(matrix),decreasing=TRUE) 
df <- data.frame(word = names(words),freq=words)

set.seed(24)
wordcloud(words = df$word, freq = df$freq, min.freq = 1,           max.words=200, random.order=FALSE, rot.per=0.35,            colors=brewer.pal(8, "Dark2"))
```

# Descriptives

## Stability

```{r}
psych::describe.by(fullShort$Stability, fullShort$Time, na.rm=T)
psych::describe(fullShort$Stability,na.rm=T)
```

## Proportion Added

```{r}
psych::describe.by(fullShort$totPropAdded, fullShort$Time, na.rm=T)
psych::describe(fullShort$totPropAdded,na.rm=T)
```

## Proportion Dropped

```{r}
psych::describe.by(fullShort$totPropDropped, fullShort$Time, na.rm=T)
psych::describe(fullShort$totPropDropped,na.rm=T)
```

# Number of Identities

```{r}
psych::describe(fullShort$numID)
```

# Degree

```{r}
psych::describe.by(fullData$degree, fullShort$Time, na.rm=T)
psych::describe(fullData$degree,na.rm=T)
```

# Strength

```{r}
psych::describe.by(fullData$strength, fullData$Time, na.rm=T)
psych::describe(fullData$strength,na.rm=T)
```

# Between Category Differences

## Degree Centrality Between Categories

```{r}
m<-glmer(degree ~  Categ + numID + Time.Z + ( 1 | subID) + ( 1 | identity:subID), data=fullData, family = poisson)
summary(m)
psych::describe.by(fullData$degree, fullData$Categ)
ggpredict(m, terms = c("Categ")) %>% plot()
comparisons(m, type = "link") %>% tidy()
```

```{r}
m<-lmer(strength.Z ~  Categ + numID + Time.Z + ( 1 | subID) + ( 1 | identity:subID), data=fullData)
summary(m)
psych::describe.by(fullData$strength, fullData$Categ)
ggpredict(m, terms = c("Categ")) %>% plot()
```

```{r, echo=FALSE}
fullData %>% drop_na %>% ggplot(aes(Categ, degree)) + 
  ggdist::stat_halfeye(adjust = .5, width = .7, .width = 0, justification = -.2, point_colour = NA) +
  geom_boxplot(width = .2, outlier.shape = NA) + 
  geom_jitter(width = .05, alpha = .3) + labs(y="Degree Centrality",x="Category") + jtools::theme_apa()
```

## Identification Between Categories

```{r}
#m<-brm(I ~ Categ + numID + Time.Z + ( Time.Z | identity / subID), data=fullData, silent=2, refresh=0, cores=ncores, refresh=0, family = cumulative("probit"))

m<-lmer(I.Z ~  Categ + numID + Time.Z + ( 1 | subID) + ( 1 | identity:subID), data=fullData)
summary(m)
psych::describe.by(as.numeric(fullData$I), fullData$Categ)
ggpredict(m, terms = c("Categ")) %>% plot()
```

# Selection Effects

## Possible Selection Models

```{r}
# Residualized Change

m<-glmer(degree ~   numID + deg_Prev + GExp.Z + BExp.Z + Time.Z + ( Time.Z + GExp.Z + BExp.Z | subID) + (1 | subID:identity), data=fullData, family=poisson)
summary(m)

m<-lmer(strength ~   numID + streng_Prev + GExp.Z + BExp.Z + Time.Z + ( Time.Z + GExp.Z + BExp.Z | subID) + (1 | subID:identity), data=fullData)
summary(m)

# Change Score/Residualized Change

m<-lmer(deg_Change ~   numID + deg_Prev + GExp.Z + BExp.Z + Time.Z + ( Time.Z + GExp.Z + BExp.Z | subID) + (1 | subID:identity), data=fullData)
summary(m)

m<-lmer(streng_Change ~   numID + streng_Prev + GExp.Z + BExp.Z + Time.Z + ( Time.Z + GExp.Z + BExp.Z | subID) + (1 | subID:identity), data=fullData)
summary(m)

# Change Score

m<-lmer(deg_Change ~   numID + GExp.Z * BExp.Z + Time.Z + ( Time.Z + GExp.Z + BExp.Z | subID) + (1 | subID:identity), data=fullData)
summary(m)

m<-lmer(streng_Change ~   numID + GExp.Z + BExp.Z + Time.Z + ( Time.Z + GExp.Z + BExp.Z | subID) + (1 | subID:identity), data=fullData)
summary(m)

# N-Back Prediction

m<-glmer(degree ~   numID + scale(GExp_Prev) + Time.Z + ( Time.Z + scale(GExp_Prev) | subID) + (1 | subID:identity), data=fullData, family=poisson)
summary(m)

# Cumulative

m<-glmer(degree ~   numID + GExp_Cum + Time.Z + ( Time.Z + GExp_Cum | subID) + (1 | subID:identity), data=fullData, family=poisson)
summary(m)
```

## Valenced Experiences

```{r}
m<-lmer( streng_Change ~   numID + MemUnc_Change.Z + ( Time.Z + MemUnc_Change.Z | subID) + (1 | subID:identity), data=fullData)
summary(m)

m<-lmer( streng_Change ~   numID + P_Change.Z + ( Time.Z + P_Change.Z | subID) + (1 | subID:identity), data=fullData)
summary(m)
```

```{r}
m<-lmer( P_Change.Z ~ numID + GExp.Z + Time.Z + Time.Z + ( Time.Z + GExp_Change.Z | subID) + (1 | subID:identity), data=fullData)
summary(m)

m<-lmer( nodPropDropped ~   numID + P_Change.Z + Time.Z + Time.Z + ( Time.Z + P.Z+GExp_Change.Z | subID) + (1 | subID:identity), data=fullData)
summary(m)

m<-lmer( nodPropAdded ~   numID + P.Z *GExp_Change.Z + Time.Z + ( Time.Z + streng_Change.Z | subID) + (1 | subID:identity), data=fullData)
summary(m)
```



```{r}
# Identity Uncertainty

m<-lmer( nodPropAdded ~   numID + IdUnc_Change.Z + Time.Z + ( Time.Z + IdUnc_Change.Z | subID) + (1 | subID:identity), data=fullData)
summary(m)

m<-lmer( nodPropDropped ~   numID + IdUnc_Change.Z * Time.Z + ( Time.Z + IdUnc_Change.Z | subID) + (1 | subID:identity), data=fullData)
summary(m)

m<-lmer( nodPropAdded ~   numID + Ent_Change.Z + Time.Z + ( Time.Z + Ent_Change.Z | subID) + (1 | subID:identity), data=fullData)
summary(m)

m<-lmer( nodPropDropped ~   numID + Ent_Change.Z * Time.Z + ( Time.Z + Ent_Change.Z | subID) + (1 | subID:identity), data=fullData)
summary(m)

m<-lmer( nodPropAdded ~   numID + P_Change.Z + Time.Z + ( Time.Z + P_Change.Z | subID) + (1 | subID:identity), data=fullData)
summary(m)

m<-lmer( nodPropDropped ~   numID + P_Change.Z * Time.Z + ( Time.Z + P_Change.Z | subID) + (1 | subID:identity), data=fullData)
summary(m)

m<-lmer( nodPropAdded ~   numID + GExp.Z * GExp_Prev.Z + Time.Z + ( Time.Z + GExp.Z + GExp_Prev.Z | subID) + (1 | subID:identity), data=fullData)
summary(m)

m<-lmer( nodPropDropped ~   numID + GExp.Z * GExp_Prev.Z + Time.Z + ( Time.Z + GExp.Z + GExp_Prev.Z | subID) + (1 | subID:identity), data=fullData)
summary(m)

m<-lmer( nodPropAdded ~   numID + BExp.Z * BExp_Prev.Z + Time.Z + ( Time.Z + BExp.Z + BExp_Prev.Z | subID) + (1 | subID:identity), data=fullData)
summary(m)

m<-lmer( nodPropDropped ~   numID + BExp.Z * BExp_Prev.Z + Time.Z + ( Time.Z + BExp.Z + BExp_Prev.Z | subID) + (1 | subID:identity), data=fullData)
summary(m)
```


Positive social identity experiences lead to increases in connections and similarities to other identities.

```{r}
m<-lmer(deg_Change ~   numID + deg_Prev + GExp.Z + BExp.Z + Time.Z + ( Time.Z + GExp.Z + BExp.Z | subID) + (1 | subID:identity), data=fullData)
summary(m)

m<-lmer(streng_Change ~   numID + streng_Prev + GExp.Z + BExp.Z + Time.Z + ( Time.Z + GExp.Z + BExp.Z | subID) + (1 | subID:identity), data=fullData)
summary(m)

# 60686 canonical example
```

## Salient Experiences

Salient identity experiences predict increases in connections and similarities to other identities

```{r}
m<-lmer(deg_Change ~   numID + deg_Prev + Salient.Z + Time.Z + ( Time.Z + Salient.Z | subID) + (1 | subID:identity), data=fullData)
summary(m)
test<-coef(m)
test$subID[order(test$subID$Salient.Z),]
# 606789 is canonical example

m<-lmer(streng_Change ~   numID + streng_Prev + Salient.Z + Time.Z + ( Time.Z + Salient.Z | subID) + (1 | subID:identity), data=fullData)
summary(m)
```

## Obligation

The more people feel they should behave like their group, the more connections and similarity to other identities increases.

```{r}
m<-lmer(deg_Change ~   numID + deg_Prev + Should.Z + Time.Z + ( Time.Z + Should.Z | subID) + (1 | subID:identity), data=fullData)
summary(m)

m<-lmer(streng_Change ~   numID + streng_Prev + Should.Z + Time.Z + ( Time.Z + Should.Z | subID) + (1 | subID:identity), data=fullData)
summary(m)
```

## Consistent Experiences

The more people feel they behaved conistent with their group, the more connections and similarity to other identities increases.

```{r}
m<-lmer(deg_Change ~   numID + deg_Prev + Consist.Z + Time.Z + ( Time.Z + Consist.Z | subID) + (1 | subID:identity), data=fullData)
summary(m)

m<-lmer(streng_Change ~   numID + streng_Prev + Consist.Z + Time.Z + ( Time.Z + Consist.Z | subID) + (1 | subID:identity), data=fullData)
summary(m)
```

## Importance

The more important is for people to belong to this group, the more connections and similarities to the group increase.

```{r}
m<-lmer(deg_Change ~   numID + deg_Prev + Ideal.Z + Time.Z + ( Time.Z + Ideal.Z | subID) + (1 | subID:identity), data=fullData)
summary(m)

m<-lmer(streng_Change ~   numID + streng_Prev + Ideal.Z + Time.Z + ( Time.Z + Ideal.Z | subID) + (1 | subID:identity), data=fullData)
summary(m)
```

## Entitativity

The more entitative/cohesive the group is perceived as being, the more connections/similarities to other groups.

```{r}
m<-lmer(deg_Change ~   numID + deg_Prev + Ent.Z + Time.Z + ( Time.Z + Ent.Z | subID) + (1 | subID:identity), data=fullData)
summary(m)

m<-lmer(streng_Change ~   numID + streng_Prev + Ent.Z + Time.Z + ( Time.Z + Ent.Z | subID) + (1 | subID:identity), data=fullData)
summary(m)
```

## Identity Uncertainty

No evidence that identity uncertainty leads to structural changes

```{r}
m<-lmer(deg_Change ~   numID + deg_Prev + IdUnc.Z + Time.Z + ( Time.Z + IdUnc.Z | subID) + (1 | subID:identity), data=fullData)
summary(m)

m<-lmer(streng_Change ~   numID + streng_Prev + IdUnc.Z + Time.Z + ( Time.Z + IdUnc.Z | subID) + (1 | subID:identity), data=fullData)
summary(m)
```

## Membership Uncertainty

No evidence that membership uncertainty leads to structural changes

```{r}
m<-lmer(deg_Change ~   numID + deg_Prev + MemUnc.Z + Time.Z + ( Time.Z + MemUnc.Z | subID) + (1 | subID:identity), data=fullData)
summary(m)

m<-lmer(streng_Change ~   numID + streng_Prev + MemUnc.Z + Time.Z + ( Time.Z + MemUnc.Z | subID) + (1 | subID:identity), data=fullData)
summary(m)
```

# Influence Effects

## Identification

```{r}
m<-lmer(I_Change ~  numID + deg_Change + Time.Z + I_Prev + ( Time.Z + deg_Change | subID) + (1 | subID:identity), data=fullData)
summary(m)

m<-lmer(I_Change ~  numID + streng_Change + Time.Z + I_Prev + ( Time.Z + streng_Change | subID) + (1 | subID:identity), data=fullData)
summary(m)
```

# Entitativity

Weak evidence that increases in degree and similarity lead to small changes in entitativity

```{r}
m<-lmer(Ent_Change ~  numID + deg_Change + Time.Z + Ent_Prev + ( Time.Z + deg_Change | subID) + (1 | subID:identity), data=fullData)
summary(m)

m<-lmer(Ent_Change ~  numID + streng_Change + Time.Z + Ent_Prev + ( Time.Z + streng_Change | subID) + (1 | subID:identity), data=fullData)
summary(m)
```

## Positivity

Small evidence that increases in strength lead to increases in positivity

```{r}
m<-lmer(P_Change ~  numID + deg_Change + Time.Z + P_Prev + ( Time.Z + deg_Change | subID) + (1 | subID:identity), data=fullData)
summary(m)

m<-lmer(P_Change ~  numID + streng_Change + Time.Z + P_Prev + ( Time.Z + streng_Change | subID) + (1 | subID:identity), data=fullData)
summary(m)
```

## Homogeneity/Similarity

No evidence that changes in degree/strength predict changes in perceived group homogeneity

```{r}
m<-lmer(Sim_Change ~  numID + deg_Change + Time.Z + Sim_Prev + ( Time.Z + deg_Change | subID) + (1 | subID:identity), data=fullData)
summary(m)

m<-lmer(Sim_Change ~  numID + streng_Change + Time.Z + Sim_Prev + ( Time.Z + streng_Change | subID) + (1 | subID:identity), data=fullData)
summary(m)
```

## Assimilation

No evidence that changes in degree/strength predict changes in perceived assimilation

```{r}
m<-lmer(A_Change ~  numID + deg_Change + Time.Z + A_Prev + ( Time.Z + deg_Change | subID) + (1 | subID:identity), data=fullData)
summary(m)

m<-lmer(A_Change ~  numID + streng_Change + Time.Z + A_Prev + ( Time.Z + streng_Change | subID) + (1 | subID:identity), data=fullData)
summary(m)
```

## Distinctness

Increases in degree and strength don't predict changes in group distinctness

```{r}
m<-lmer(D_Change ~  numID + deg_Change + Time.Z + A_Prev + ( Time.Z + deg_Change | subID) + (1 | subID:identity), data=fullData)
summary(m)

m<-lmer(D_Change ~  numID + streng_Change + Time.Z + A_Prev + ( Time.Z + streng_Change | subID) + (1 | subID:identity), data=fullData)
summary(m)
```

# Degree Centrality Effects

## Degree Centrality Predicts Strength of Identification

```{r}
m<-lmer(I.Z ~  numID + Time.Z + degree + ( Time.Z | subID) + (1 | subID:identity), data=fullData)
summary(m)

m<-lmer(I.Z ~  numID + Time.Z + strength.Z + ( Time.Z | subID) + (1 | subID:identity), data=fullData)
summary(m)
```

### No Change Across Time

```{r}
m<-lmer(I.Z ~  numID + Time.Z * degree + ( Time.Z | subID) + (1 | subID:identity), data=fullData)
summary(m)

m<-lmer(I.Z ~  numID + Time.Z * strength.Z + ( Time.Z | subID) + (1 | subID:identity), data=fullData)
summary(m)
```

## Identity centrality predicts mutability

```{r}
m<-lmer(M.Z ~  numID + Time.Z + degree + ( Time.Z | subID) + (1 | subID:identity), data=fullData)
summary(m)

m<-lmer(M.Z ~  numID + Time.Z + strength.Z + ( Time.Z | subID) + (1 | subID:identity), data=fullData)
summary(m)
```

### No change across time

```{r}
m<-lmer(M.Z ~  numID + Time.Z * degree + ( Time.Z | subID) + (1 | subID:identity), data=fullData)
summary(m)

m<-lmer(M.Z ~  numID + Time.Z * strength.Z + ( Time.Z | subID) + (1 | subID:identity), data=fullData)
summary(m)
```

## Identity centrality predicts entitativity

```{r}
m<-lmer(Ent.Z ~  numID + Time.Z + degree + ( Time.Z | subID) + (1 | subID:identity), data=fullData)
summary(m)

m<-lmer(Ent.Z ~  numID + Time.Z + strength.Z + ( Time.Z | subID) + (1 | subID:identity), data=fullData)
summary(m)

```

### No change across time

```{r}
m<-lmer(Ent.Z ~  numID + Time.Z * degree + ( Time.Z | subID) + (1 | subID:identity), data=fullData)
summary(m)

m<-lmer(Ent.Z ~  numID + Time.Z * strength.Z + ( Time.Z | subID) + (1 | subID:identity), data=fullData)
summary(m)
ggpredict(m, terms = c("Time.Z","strength.Z")) %>% plot()
```

## Identity centrality predicts mutability

```{r}
m<-lmer(M.Z ~  numID + Time.Z + degree + ( Time.Z | identity / subID), data=fullData)
summary(m)

m<-lmer(M.Z ~  numID + Time.Z + strength.Z + ( Time.Z | identity / subID), data=fullData)
summary(m)
```

### No change across time

```{r}
m<-lmer(M.Z ~  numID + Time.Z * degree + ( Time.Z | identity / subID), data=fullData)
summary(m)
ggpredict(m, terms = c("Time.Z","degree")) %>% plot()

m<-lmer(M.Z ~  numID + Time.Z * strength.Z + ( Time.Z | identity / subID), data=fullData)
summary(m)
```

## Identity centrality predicts prototypicality

```{r}
m<-lmer(Proto.Z ~  numID + Time.Z + degree + ( Time.Z | identity / subID), data=fullData)
summary(m)

m<-lmer(Proto.Z ~  numID + Time.Z + strength.Z + ( Time.Z | identity / subID), data=fullData)
summary(m)
```

### No change across time

```{r}
m<-lmer(Proto.Z ~  numID + Time.Z * degree + ( Time.Z | identity / subID), data=fullData)
summary(m)

m<-lmer(Proto.Z ~  numID + Time.Z * strength.Z + ( Time.Z | identity / subID), data=fullData)
summary(m)
```

## Identity centrality predicts group homogeneity

```{r}
m<-lmer(Sim.Z ~  numID + Time.Z + degree + ( Time.Z | identity / subID), data=fullData)
summary(m)

m<-lmer(Sim.Z ~  numID + Time.Z + strength.Z + ( Time.Z | identity / subID), data=fullData)
summary(m)
```

### No change across time

```{r}
m<-lmer(Sim.Z ~  numID + Time.Z * degree + ( Time.Z | identity / subID), data=fullData)
summary(m)

m<-lmer(Sim.Z ~  numID + Time.Z * strength.Z + ( Time.Z | identity / subID), data=fullData)
summary(m)
```

## Strength (but not centrality) predicts bias

```{r}
m<-lmer(bias.Z ~  numID + Time.Z + degree + ( Time.Z | identity / subID), data=fullData)
summary(m)

m<-lmer(bias.Z ~  numID + Time.Z + strength.Z + ( Time.Z | identity / subID), data=fullData)
summary(m)
```

### Across time, less strength predicts less bias

```{r}
m<-lmer(bias.Z ~  numID + Time.Z * degree + ( Time.Z | identity / subID), data=fullData)
summary(m)
ggpredict(m, terms = c("Time.Z","degree")) %>% plot()

m<-lmer(bias.Z ~  numID + Time.Z * strength.Z + ( Time.Z | identity / subID), data=fullData)
summary(m)
ggpredict(m, terms = c("Time.Z","strength.Z")) %>% plot()
```

## Identity centrality predicts bias

```{r}
m<-lmer(bias.Z ~  numID + Time.Z + degree + ( Time.Z | identity / subID), data=fullData)
summary(m)

m<-lmer(bias.Z ~  numID + Time.Z + strength.Z + ( Time.Z | identity / subID), data=fullData)
summary(m)
```

### Across time, less strength predicts less bias

```{r}
m<-lmer(bias.Z ~  numID + Time.Z * degree + ( Time.Z | identity / subID), data=fullData)
summary(m)

m<-lmer(bias.Z ~  numID + Time.Z * strength.Z + ( Time.Z | identity / subID), data=fullData)
summary(m)
ggpredict(m, terms = c("Time.Z","strength.Z")) %>% plot()
```

## Identity centrality and strength predict positivity

```{r}
m<-lmer(P.Z ~  numID + Time.Z + degree + ( Time.Z | identity / subID), data=fullData)
summary(m)

m<-lmer(P.Z ~  numID + Time.Z + strength.Z + ( Time.Z | identity / subID), data=fullData)
summary(m)
```

### No change across time

```{r}
m<-lmer(P.Z ~  numID + Time.Z * degree + ( Time.Z | identity / subID), data=fullData)
summary(m)

m<-lmer(P.Z ~  numID + Time.Z * strength.Z + ( Time.Z | identity / subID), data=fullData)
summary(m)
ggpredict(m, terms = c("Time.Z","strength.Z")) %>% plot()
```

## Identity centrality and strength negatively predict identity uncertainty

```{r}
m<-lmer(IdUnc.Z ~  numID + Time.Z + degree + ( Time.Z | identity / subID), data=fullData)
summary(m)

m<-lmer(IdUnc.Z ~  numID + Time.Z + strength.Z + ( Time.Z | identity / subID), data=fullData)
summary(m)
```

### No change across time

```{r}
m<-lmer(IdUnc.Z ~  numID + Time.Z * degree + ( Time.Z | identity / subID), data=fullData)
summary(m)

m<-lmer(IdUnc.Z ~  numID + Time.Z * strength.Z + ( Time.Z | identity / subID), data=fullData)
summary(m)
ggpredict(m, terms = c("Time.Z","strength.Z")) %>% plot()
```

## Identity centrality and strength predict assimilation

```{r}
m<-lmer(A.Z ~  numID + Time.Z + degree + ( Time.Z | identity / subID), data=fullData)
summary(m)

m<-lmer(A.Z ~  numID + Time.Z + strength.Z + ( Time.Z | identity / subID), data=fullData)
summary(m)
```

### No change across time

```{r}
m<-lmer(A.Z ~  numID + Time.Z * degree + ( Time.Z | identity / subID), data=fullData)
summary(m)

m<-lmer(A.Z ~  numID + Time.Z * strength.Z + ( Time.Z | identity / subID), data=fullData)
summary(m)
ggpredict(m, terms = c("Time.Z","strength.Z")) %>% plot()
```

## Identity centrality and strength predict assimilation

```{r}
m<-lmer(D.Z ~  numID + Time.Z + degree + ( Time.Z | identity / subID), data=fullData)
summary(m)

m<-lmer(D.Z ~  numID + Time.Z + strength.Z + ( Time.Z | identity / subID), data=fullData)
summary(m)
```

### Identity centrality predicts more differentiation across time

```{r}
m<-lmer(D.Z ~  numID + Time.Z * degree + ( Time.Z | identity / subID), data=fullData)
summary(m)

m<-lmer(D.Z ~  numID + Time.Z * strength.Z + ( Time.Z | identity / subID), data=fullData)
summary(m)
ggpredict(m, terms = c("Time.Z","strength.Z")) %>% plot()
```

# Propagation

```{r}
m<-lmer(I_neigh.Z ~ I.Z * Time.Z + ( I.Z + Time.Z | subID ) + (1 | subID:identity), data=fullData)
summary(m)
ggpredict(m, terms = c("Time.Z","I.Z")) %>% plot()

m<-lmer(I.Z ~ I_neigh.Z + Time.Z + ( I_neigh.Z + Time.Z | subID ) + (1 | subID:identity), data=fullData)
summary(m)
ggpredict(m, terms = c("Time.Z","I_neigh.Z")) %>% plot()
```

```{r}
m<-lmer(P_neigh.Z ~ P.Z * Time.Z + ( P.Z + Time.Z | subID ) + (1 | subID:identity), data=fullData)
summary(m)
ggpredict(m, terms = c("Time.Z","P.Z")) %>% plot()

m<-lmer(P.Z ~ P_neigh.Z * Time.Z + ( P_neigh.Z + Time.Z | subID ) + (1 | subID:identity), data=fullData)
summary(m)
ggpredict(m, terms = c("Time.Z","P_neigh.Z")) %>% plot()
```

## Feelings of stigma propagate to neighbors across time

```{r}
m<-lmer(St_neigh.Z ~ St.Z * Time.Z + ( St.Z + Time.Z | subID ) + (1 | subID:identity), data=fullData)
summary(m)
ggpredict(m, terms = c("Time.Z","St.Z")) %>% plot()
```

## Prototypicality Propagates to Neighbors Across Time

```{r}
m<-lmer(Proto_neigh.Z ~ Proto.Z * Time.Z + ( Proto.Z + Time.Z | subID ) + ( Time.Z | subID:identity), data=fullData)
summary(m)
ggpredict(m, terms = c("Time.Z","Proto.Z")) %>% plot()
```
# Identity-Level Self-Report

## Assimilation predicts identification across time

````{r, echo=FALSE, warning=FALSE, include=FALSE}
# m<-brm(I ~ A.Z * Time.Z + ( A.Z + Time.Z | subID ) + (1 | identity), data=fullData, silent=2, refresh=0, cores=ncores, refresh=0, family = cumulative("logit"))

m<-lmer(I.Z ~ A.Z * Time.Z + ( A.Z + Time.Z | subID ) + (1 | identity : subID), data=fullData)
summary(m)
ggpredict(m, terms = c("Time.Z","A.Z")) %>% plot()
```

## Group Homogeneity Predicts Social Identification Across Time

````{r, echo=FALSE, warning=FALSE, include=FALSE}
# m<-brm(I ~ A.Z * Time.Z + ( A.Z + Time.Z | subID ) + (1 | identity), data=fullData, silent=2, refresh=0, cores=ncores, refresh=0, family = cumulative("logit"))

m<-lmer(I.Z ~ Sim.Z * Time.Z + ( Sim.Z + Time.Z | subID ) + (1 | identity : subID), data=fullData)
summary(m)
ggpredict(m, terms = c("Time.Z","Sim.Z")) %>% plot()
```

## Prototypicality predicts identification across time

```{r}
#m<-brm(I ~ Proto.Z * Time.Z + ( Proto.Z + Time.Z | subID ) + (1 | identity), data=fullData, silent=2, refresh=0, cores=ncores, refresh=0, family = cumulative("logit"))

m<-lmer(I.Z ~ Proto.Z * Time.Z + ( Proto.Z + Time.Z | subID ) + (1 | subID:identity), data=fullData)
summary(m)
ggpredict(m, terms = c("Time.Z","Proto.Z")) %>% plot()
```


## Obligations Towards Identity and it's Neighbor Predict Identity-Consistent Behaviors

```{r}
m<-lmer(Consist.Z ~  Should_neigh.Z + Should.Z + ( Should_neigh.Z+Should.Z | subID) + ( 1 | identity : subID), data=fullData)
summary(m)
```



# Individual Differences

## Multiple Group Membership and Well-Being (i.e., Self-Esteem)




```{r}
m <- glmer(numID~SE.Z + Time.Z 
                 + ( Time.Z |subID),
                 data=fullShort, family="poisson")
summary(m)

m <- glmer(numID~NFC.Z + Time.Z 
                 + ( Time.Z |subID),
                 data=fullShort, family="poisson")
summary(m)

m <- glmer(numID~SCC.Z + Time.Z 
                 + ( Time.Z |subID),
                 data=fullShort, family="poisson")
summary(m)
```

## Network Density

```{r}
m <- lmer(dense.Z~SE.Z + Time.Z 
                 + ( Time.Z |subID),
                 data=fullShort)
summary(m)

m <- lmer(dense.Z~NFC.Z + Time.Z 
                 + ( Time.Z |subID),
                 data=fullShort)
summary(m)

m <- lmer(numID~SCC.Z + Time.Z 
                 + ( Time.Z |subID),
                 data=fullShort)
summary(m)
```

# Positive Homophily

```{r}
m <- lmer(P_homoph.Z~SE.Z + Time.Z 
                 + ( Time.Z |subID),
                 data=fullShort)
summary(m)

m <- lmer(P_homoph.Z~NFC.Z + Time.Z 
                 + ( Time.Z |subID),
                 data=fullShort)
summary(m)

m <- lmer(P_homoph.Z~SCC.Z + Time.Z 
                 + ( Time.Z |subID),
                 data=fullShort)
summary(m)
```

# Identification Homophily

```{r}
m <- lmer(I_homoph.Z~SE.Z + Time.Z 
                 + ( Time.Z |subID),
                 data=fullShort)
summary(m)

m <- lmer(I_homoph.Z~NFC.Z + Time.Z 
                 + ( Time.Z |subID),
                 data=fullShort)
summary(m)

m <- lmer(I_homoph.Z~SCC.Z + Time.Z 
                 + ( Time.Z |subID),
                 data=fullShort)
summary(m)
```

# Membership Uncertainty Homophily

```{r}
m <- lmer(MemUnc_homoph.Z~SE.Z + Time.Z 
                 + ( Time.Z |subID),
                 data=fullShort)
summary(m)

m <- lmer(MemUnc_homoph.Z~NFC.Z + Time.Z 
                 + ( Time.Z |subID),
                 data=fullShort)
summary(m)

m <- lmer(MemUnc_homoph.Z~SCC.Z + Time.Z 
                 + ( Time.Z |subID),
                 data=fullShort)
summary(m)
```

# Entitativity Homophily

```{r}
m <- lmer(Ent_homoph.Z~SE.Z + Time.Z 
                 + ( Time.Z |subID),
                 data=fullShort)
summary(m)

m <- lmer(Ent_homoph.Z~NFC.Z + Time.Z 
                 + ( Time.Z |subID),
                 data=fullShort)
summary(m)

m <- lmer(Ent_homoph.Z~SCC.Z + Time.Z 
                 + ( Time.Z |subID),
                 data=fullShort)
summary(m)
```




