---
title: "Longitudinal Identity Network Paper Results"
output: html_notebook
---

# Import and Prepare

```{r, echo=FALSE, include=FALSE}
library(groundhog)
pkgs <-  c("tidyverse","here", "lmerTest", "sjPlot","broom.mixed", "kableExtra", "ggeffects", "gt", "brms", "bayestestR","ggdist")
groundhog.day <- '2022-07-25'
groundhog.library(pkgs, groundhog.day)
here::i_am("Analyses/idNetPrelimAnalyses.Rmd")
```

```{r, include=FALSE}
fullLong <- read.csv(here("Data/longIdentityNet.csv"))
fullShort <- read.csv(here("Data/shortIdentityNet.csv"))
fullData <- fullLong %>% full_join(fullShort, by = c("subID","Time"))

indDiffs <- fullData[!duplicated(fullData$subID),]
```

```{r,include=FALSE}
scaled <- apply(fullData[6:ncol(fullData)], 2, function(x) scale(x))
colnames(scaled) <- paste0(colnames(scaled),".Z")
fullData <- cbind(fullData, scaled)


scaled <- apply(fullShort[2:ncol(fullShort)], 2, function(x) scale(x))
colnames(scaled) <- paste0(colnames(scaled),".Z")
fullShort <- cbind(fullShort, scaled)

fullData <- fullData %>% mutate_at(c("Salient", "I", "M", "I", "P", "St", "Ent", "Sim", "Proto", "A", "D", "MemUnc", "IdUnc", "Should", "Consist", "Salient", "Ideal", "BExp", "GExp", "BelPer"), ordered)
```

```{r, include=FALSE}
ncores = parallel::detectCores()
options(mc.cores = parallel::detectCores())
```

```{r, include=FALSE}
named.contr.sum<-function(x, ...) {
    if (is.factor(x)) {
        x <- levels(x)
    } else if (is.numeric(x) & length(x)==1L) {
        stop("cannot create names with integer value. Pass factor levels")
    }
    x<-contr.sum(x, ...)
    colnames(x) <- apply(x,2,function(x) 
         paste(names(x[x>0]), names(x[x<0]), sep="-")
    )
    x
}
fullData$Categ <- as.factor(fullData$Categ)
contrasts(fullData$Categ) <- named.contr.sum(levels(fullData$Categ))
```

# Between Category Differences

## Degree Centrality Between Categories

```{r}
m<-glmer(degree ~  Categ + numID + Time.Z + ( Time.Z | identity / subID), data=fullData, family = poisson)
summary(m)
ggpredict(m, terms = c("Categ")) %>% plot()
```

```{r}
m<-lmer(strength.Z ~  Categ + numID + Time.Z + ( Time.Z | identity / subID), data=fullData)
summary(m)
ggpredict(m, terms = c("Categ")) %>% plot()
```

```{r, echo=FALSE}
fullData %>% drop_na %>% ggplot(aes(Categ, degree)) + 
  ggdist::stat_halfeye(adjust = .5, width = .7, .width = 0, justification = -.2, point_colour = NA) +
  geom_boxplot(width = .2, outlier.shape = NA) + 
  geom_jitter(width = .05, alpha = .3) + labs(y="Degree Centrality",x="Category") + jtools::theme_apa()
```

## Identification Between Categories

```{r}
#m<-brm(I ~ Categ + numID + Time.Z + ( Time.Z | identity / subID), data=fullData, silent=2, refresh=0, cores=ncores, refresh=0, family = cumulative("probit"))

m<-lmer(I.Z ~  Categ + numID + Time.Z + ( Time.Z | identity / subID), data=fullData)
summary(m)
ggpredict(m, terms = c("Categ")) %>% plot()
```

# Degree Centrality Effects

## Degree Centrality Predicts Strength of Identification

```{r}
m<-lmer(I.Z ~  numID + Time.Z + degree + ( Time.Z | identity / subID), data=fullData)
summary(m)

m<-lmer(I.Z ~  numID + Time.Z + strength.Z + ( Time.Z | identity / subID), data=fullData)
summary(m)
```

### No Change Across Time

```{r}
m<-lmer(I.Z ~  numID + Time.Z * degree + ( Time.Z | identity / subID), data=fullData)
summary(m)

m<-lmer(I.Z ~  numID + Time.Z * strength.Z + ( Time.Z | identity / subID), data=fullData)
summary(m)
```

## Identity centrality predicts mutability

```{r}
m<-lmer(M.Z ~  numID + Time.Z + degree + ( Time.Z | identity / subID), data=fullData)
summary(m)

m<-lmer(M.Z ~  numID + Time.Z + strength.Z + ( Time.Z | identity / subID), data=fullData)
summary(m)
```

### No change across time

```{r}
m<-lmer(M.Z ~  numID + Time.Z * degree + ( Time.Z | identity / subID), data=fullData)
summary(m)

m<-lmer(M.Z ~  numID + Time.Z * strength.Z + ( Time.Z | identity / subID), data=fullData)
summary(m)
```

## Identity centrality predicts entitativity

```{r}
m<-lmer(Ent.Z ~  numID + Time.Z + degree + ( Time.Z | identity / subID), data=fullData)
summary(m)

m<-lmer(Ent.Z ~  numID + Time.Z + strength.Z + ( Time.Z | identity / subID), data=fullData)
summary(m)
```

### No change across time

```{r}
m<-lmer(Ent.Z ~  numID + Time.Z * degree + ( Time.Z | identity / subID), data=fullData)
summary(m)

m<-lmer(Ent.Z ~  numID + Time.Z * strength.Z + ( Time.Z | identity / subID), data=fullData)
summary(m)
```

## Identity centrality predicts mutability

```{r}
m<-lmer(M.Z ~  numID + Time.Z + degree + ( Time.Z | identity / subID), data=fullData)
summary(m)

m<-lmer(M.Z ~  numID + Time.Z + strength.Z + ( Time.Z | identity / subID), data=fullData)
summary(m)
```

### No change across time

```{r}
m<-lmer(M.Z ~  numID + Time.Z * degree + ( Time.Z | identity / subID), data=fullData)
summary(m)

m<-lmer(M.Z ~  numID + Time.Z * strength.Z + ( Time.Z | identity / subID), data=fullData)
summary(m)
```

## Identity centrality predicts prototypicality

```{r}
m<-lmer(Proto.Z ~  numID + Time.Z + degree + ( Time.Z | identity / subID), data=fullData)
summary(m)

m<-lmer(Proto.Z ~  numID + Time.Z + strength.Z + ( Time.Z | identity / subID), data=fullData)
summary(m)
```

### No change across time

```{r}
m<-lmer(Proto.Z ~  numID + Time.Z * degree + ( Time.Z | identity / subID), data=fullData)
summary(m)

m<-lmer(Proto.Z ~  numID + Time.Z * strength.Z + ( Time.Z | identity / subID), data=fullData)
summary(m)
```

## Identity centrality predicts group homogeneity

```{r}
m<-lmer(Sim.Z ~  numID + Time.Z + degree + ( Time.Z | identity / subID), data=fullData)
summary(m)

m<-lmer(Sim.Z ~  numID + Time.Z + strength.Z + ( Time.Z | identity / subID), data=fullData)
summary(m)
```

### No change across time

```{r}
m<-lmer(Sim.Z ~  numID + Time.Z * degree + ( Time.Z | identity / subID), data=fullData)
summary(m)

m<-lmer(Sim.Z ~  numID + Time.Z * strength.Z + ( Time.Z | identity / subID), data=fullData)
summary(m)
```

## Strength (but not centrality) predicts bias

```{r}
m<-lmer(bias.Z ~  numID + Time.Z + degree + ( Time.Z | identity / subID), data=fullData)
summary(m)

m<-lmer(bias.Z ~  numID + Time.Z + strength.Z + ( Time.Z | identity / subID), data=fullData)
summary(m)
```

### Across time, less strength predicts less bias

```{r}
m<-lmer(bias.Z ~  numID + Time.Z * degree + ( Time.Z | identity / subID), data=fullData)
summary(m)

m<-lmer(bias.Z ~  numID + Time.Z * strength.Z + ( Time.Z | identity / subID), data=fullData)
summary(m)
ggpredict(m, terms = c("Time.Z","strength.Z")) %>% plot()
```

## Identity centrality predicts bias

```{r}
m<-lmer(bias.Z ~  numID + Time.Z + degree + ( Time.Z | identity / subID), data=fullData)
summary(m)

m<-lmer(bias.Z ~  numID + Time.Z + strength.Z + ( Time.Z | identity / subID), data=fullData)
summary(m)
```

### Across time, less strength predicts less bias

```{r}
m<-lmer(bias.Z ~  numID + Time.Z * degree + ( Time.Z | identity / subID), data=fullData)
summary(m)

m<-lmer(bias.Z ~  numID + Time.Z * strength.Z + ( Time.Z | identity / subID), data=fullData)
summary(m)
ggpredict(m, terms = c("Time.Z","strength.Z")) %>% plot()
```

## Identity centrality and strength predict positivity

```{r}
m<-lmer(P.Z ~  numID + Time.Z + degree + ( Time.Z | identity / subID), data=fullData)
summary(m)

m<-lmer(P.Z ~  numID + Time.Z + strength.Z + ( Time.Z | identity / subID), data=fullData)
summary(m)
```

### No change across time

```{r}
m<-lmer(P.Z ~  numID + Time.Z * degree + ( Time.Z | identity / subID), data=fullData)
summary(m)

m<-lmer(P.Z ~  numID + Time.Z * strength.Z + ( Time.Z | identity / subID), data=fullData)
summary(m)
ggpredict(m, terms = c("Time.Z","strength.Z")) %>% plot()
```

## Identity centrality and strength negatively predict identity uncertainty

```{r}
m<-lmer(IdUnc.Z ~  numID + Time.Z + degree + ( Time.Z | identity / subID), data=fullData)
summary(m)

m<-lmer(IdUnc.Z ~  numID + Time.Z + strength.Z + ( Time.Z | identity / subID), data=fullData)
summary(m)
```

### No change across time

```{r}
m<-lmer(IdUnc.Z ~  numID + Time.Z * degree + ( Time.Z | identity / subID), data=fullData)
summary(m)

m<-lmer(IdUnc.Z ~  numID + Time.Z * strength.Z + ( Time.Z | identity / subID), data=fullData)
summary(m)
ggpredict(m, terms = c("Time.Z","strength.Z")) %>% plot()
```

## Identity centrality and strength predict assimilation

```{r}
m<-lmer(A.Z ~  numID + Time.Z + degree + ( Time.Z | identity / subID), data=fullData)
summary(m)

m<-lmer(A.Z ~  numID + Time.Z + strength.Z + ( Time.Z | identity / subID), data=fullData)
summary(m)
```

### No change across time

```{r}
m<-lmer(A.Z ~  numID + Time.Z * degree + ( Time.Z | identity / subID), data=fullData)
summary(m)

m<-lmer(A.Z ~  numID + Time.Z * strength.Z + ( Time.Z | identity / subID), data=fullData)
summary(m)
ggpredict(m, terms = c("Time.Z","strength.Z")) %>% plot()
```

## Identity centrality and strength predict assimilation

```{r}
m<-lmer(D.Z ~  numID + Time.Z + degree + ( Time.Z | identity / subID), data=fullData)
summary(m)

m<-lmer(D.Z ~  numID + Time.Z + strength.Z + ( Time.Z | identity / subID), data=fullData)
summary(m)
```

### Identity centrality predicts more differentiation across time

```{r}
m<-lmer(D.Z ~  numID + Time.Z * degree + ( Time.Z | identity / subID), data=fullData)
summary(m)

m<-lmer(D.Z ~  numID + Time.Z * strength.Z + ( Time.Z | identity / subID), data=fullData)
summary(m)
ggpredict(m, terms = c("Time.Z","strength.Z")) %>% plot()
```

# Propagation

## Feelings of stigma propagate to neighbors across time

```{r}
m<-lmer(St_neigh.Z ~ St.Z * Time.Z + ( St.Z + Time.Z | subID ) + (1 | subID:identity), data=fullData)
summary(m)
ggpredict(m, terms = c("Time.Z","St.Z")) %>% plot()
```

## Prototypicality Propagates to Neighbors Across Time

```{r}
m<-lmer(Proto_neigh.Z ~ Proto.Z * Time.Z + ( Proto.Z + Time.Z | subID ) + ( Time.Z | subID:identity), data=fullData)
summary(m)
ggpredict(m, terms = c("Time.Z","Proto.Z")) %>% plot()
```
# Identity-Level Self-Report

## Assimilation predicts identification across time

````{r, echo=FALSE, warning=FALSE, include=FALSE}
# m<-brm(I ~ A.Z * Time.Z + ( A.Z + Time.Z | subID ) + (1 | identity), data=fullData, silent=2, refresh=0, cores=ncores, refresh=0, family = cumulative("logit"))

m<-lmer(I.Z ~ A.Z * Time.Z + ( A.Z + Time.Z | subID ) + (1 | identity : subID), data=fullData)
summary(m)
ggpredict(m, terms = c("Time.Z","A.Z")) %>% plot()
```

## Group Homogeneity Predicts Social Identification Across Time

````{r, echo=FALSE, warning=FALSE, include=FALSE}
# m<-brm(I ~ A.Z * Time.Z + ( A.Z + Time.Z | subID ) + (1 | identity), data=fullData, silent=2, refresh=0, cores=ncores, refresh=0, family = cumulative("logit"))

m<-lmer(I.Z ~ Sim.Z * Time.Z + ( Sim + Time.Z | subID ) + (1 | identity : subID), data=fullData)
summary(m)
ggpredict(m, terms = c("Time.Z","Sim")) %>% plot()
```

## Prototypicality predicts identification across time

```{r}
#m<-brm(I ~ Proto.Z * Time.Z + ( Proto.Z + Time.Z | subID ) + (1 | identity), data=fullData, silent=2, refresh=0, cores=ncores, refresh=0, family = cumulative("logit"))

m<-lmer(I.Z ~ Proto.Z * Time.Z + ( Proto.Z + Time.Z | subID ) + (1 | subID:identity), data=fullData)
summary(m)
ggpredict(m, terms = c("Time.Z","Proto.Z")) %>% plot()
```


## Obligations Towards Identity and it's Neighbor Predict Identity-Consistent Behaviors

```{r}
m<-lmer(Consist.Z ~  Should_neigh.Z + Should.Z + ( Should_neigh.Z+Should.Z | subID) + ( 1 | identity : subID), data=fullData)
summary(m)
```

## Feling like you are obligated to act identity-consistent predicts identity-consistency

```{r}
m<-lmer(Consist.Z ~ Should.Z * Time.Z + ( Should.Z + Time.Z | subID ) + ( Time.Z | subID:identity), data=fullData)
summary(m)
ggpredict(m, terms = c("Time.Z","Should.Z")) %>% plot()
```

# Individual Differences

## Multiple Group Membership and Well-Being (i.e., Self-Esteem)

```{r}
m <- glmer(numID~SE.Z * Time.Z 
                 + ( Time.Z |subID),
                 data=fullShort, family="poisson")
summary(m)

m <- glmer(numID~NFC.Z * Time.Z 
                 + ( Time.Z |subID),
                 data=fullShort, family="poisson")
summary(m)

m <- glmer(numID~SCC.Z * Time.Z 
                 + ( Time.Z |subID),
                 data=fullShort, family="poisson")
summary(m)
```

## Network Density

```{r}
m <- lmer(dense.Z~SE.Z * Time.Z 
                 + ( Time.Z |subID),
                 data=fullShort)
summary(m)

m <- lmer(dense.Z~NFC.Z * Time.Z 
                 + ( Time.Z |subID),
                 data=fullShort)
summary(m)

m <- lmer(numID~SCC.Z * Time.Z 
                 + ( Time.Z |subID),
                 data=fullShort)
summary(m)
```

```{r}
```




