---
title: "idNetLong"
author: "Elder, Jacob"
date: "2022-09-13"
output: html_document
---

```{r setup, include=FALSE}
library(groundhog)
pkgs <-  c("tidyverse","here", "igraph","lmerTest")
groundhog.day <- '2022-07-25'
groundhog.library(pkgs, groundhog.day)
here::i_am("Analyses/idNetPrelimAnalyses.Rmd")
```

```{r}
fullLong <- read.csv(here("Data/longIdentityNet.csv"))
fullShort <- read.csv(here("Data/shortIdentityNet.csv"))
fullData <- fullLong %>% full_join(fullShort, by = c("subID","Time"))
```

# Pre-Registered

## Salient identity-relevant events predict greater social identification

```{r}
m<-lmer(I ~ Salient + ( Salient | subID ) + (1 | identity), data=fullLong)
summary(m)
```
### Across time

```{r}
m<-lmer(I ~ Salient*Time + ( Salient + Time | subID ) + (1 | identity), data=fullLong)
summary(m)
ggpredict(m, c("Time","Salient")) %>% plot()
```

## Positive experiences lead to more social identification

```{r}
m<-lmer(I ~ GExp + ( GExp | subID ) + (1 | identity), data=fullLong)
summary(m)
```

### Across time

```{r}
m<-lmer(I ~ GExp * Time + ( GExp + Time | subID ) + (1 | identity), data=fullLong)
summary(m)
```
# Negative experiences do not lead to less social identification

```{r}
m<-lmer(I ~ BExp + ( BExp | subID ) + (1 | identity), data=fullLong)
summary(m)
```
### Across time

```{r}
m<-lmer(I ~ BExp * Time + ( BExp + Time | subID ) + (1 | identity), data=fullLong)
summary(m)
```

## Changes to one identity will result in changes to other connected identities

### Positivity

As identity perceived more positively, it's neighboring connected identities are also perceived more positively

```{r}
m<-lmer(P_neigh ~ P * Time + ( P + Time | subID ) + (1 | identity), data=fullLong)
summary(m)
ggpredict(m, c("Time","P[1,4,7]")) %>% plot()
```

# Identity Uncertainty

```{r}
m<-lmer(IdUnc_neigh ~ IdUnc + ( IdUnc | subID ) + (1 | identity), data=fullLong)
summary(m)
```

# Prototypicality

```{r}
m<-lmer(Proto_neigh ~ Proto + ( Proto | subID ) + (1 | identity), data=fullLong)
summary(m)
```
# Acting consistent with connected identities increases identification with target identity

```{r}
m<-lmer(I ~ Consist_neigh + ( Consist_neigh | subID ) + (1 | identity), data=fullLong)
summary(m)
```

# Feeling it is important to belong to neighboring identity is associated with greater identification with target identity

```{r}
m<-lmer(I ~ Ideal_neigh + ( Ideal_neigh | subID ) + (1 | identity), data=fullLong)
summary(m)
```

# Stigma to connected identities is associated with increase in feeling categorized

```{r}
m<-lmer(BelPer ~ St_neigh + ( St_neigh  | subID ) + (1 | identity), data=fullLong)
summary(m)
```


#

```{r}
m<-lmer(Proto_neigh ~ Proto + ( Proto | subID ) + (1 | identity), data=fullLong)
summary(m)
```

## Feelings obligated to behave in-line with identity increases identification with connected identities

```{r}
m<-lmer(I_neigh ~ Should + ( Should | subID ) + (1 | identity), data=fullLong)
summary(m)
```


## People will change their identities, feelings about an identity, and relations to that identity, when experiencing events or experiences that are continually inconsistent with the identity

```{r}
m<-lmer(I ~ Consist + ( Consist | subID ) + (1 | identity), data=fullLong)
summary(m)
```
## If people experience negative feelings or events associated with one identity, they will de-identify with identities or change the relationships previously associated with that identity

```{r}
m<-lmer(I ~ BExp * GExp + ( BExp + GExp | subID ) + (1 | identity), data=fullLong)
summary(m)
ggpredict(m, c("BExp","GExp")) %>% plot()
```

## If people experience a discrepancy between their ideal and actual self, they will seek to resolve it by changing their identities

```{r}
m<-lmer(I ~ discrep * Time + ( discrep | subID ) + (1 | identity), data=fullLong)
summary(m)
```

## Higher uncertainty will predict greater identification, especially for entitative groups: Nope

```{r}
m<-lmer(I ~ MemUnc + ( MemUnc | subID ) + (1 | identity), data=fullLong)
summary(m)

m<-lmer(I ~ IdUnc + ( IdUnc | subID ) + (1 | identity), data=fullLong)
summary(m)
```

### Especially for entitative identities

```{r}
m<-lmer(I ~ MemUnc * Ent + ( MemUnc + Ent | subID ) + (1 | identity), data=fullLong)
summary(m)

m<-lmer(I ~ IdUnc * Ent + ( IdUnc + Ent | subID ) + (1 | identity), data=fullLong)
summary(m)
```

## Entitativity predicts social identification

```{r}
m<-lmer(I ~ Ent + ( Ent | subID ) + (1 | identity), data=fullLong)
summary(m)
```

## Optimal Distinctiveness predicts social identification

```{r}
m<-lmer(I ~ A * D + ( A + D | subID ) + (1 | identity), data=fullLong)
summary(m)
ggpredict(m, c("A","D")) %>% plot()
```
# Exploratory

## Cumulative inconsistency predicts disidentification

```{r}
m<-lmer(I ~ Consist_Cum + Time + ( Consist_Cum+Time | subID ) + (1 | identity), data=fullLong)
summary(m)
```

## Cumulative salient experiences

```{r}
m<-lmer(I ~ Salient_Cum + Time + ( Salient_Cum+Time | subID ) + (1 | identity), data=fullLong)
summary(m)
```

## Both cumulative salient and consistent modeled simultaneously

```{r}
m<-lmer(I ~ Salient_Cum + Time + Consist_Cum + ( Salient_Cum+Time+Consist_Cum | subID ) + (1 | identity), data=fullLong)
summary(m)
```




```{r}
m<-lmer(I ~ MemUnc_Cum * Time + ( MemUnc_Cum+Time | subID ) + (1 | identity), data=fullLong)
summary(m)

m<-lmer(I ~ IdUnc_Cum * Time + ( IdUnc_Cum+Time | subID ) + (1 | identity), data=fullLong)
summary(m)

m
```


## Degree centrality predicts identification

```{r}
m<-lmer(Degree ~ Salient + ( Salient | subID ) + (1 | identity), data=fullLong)
summary(m)

m<-lmer(Degree ~ I + ( I | subID ) + (1 | identity), data=fullLong)
summary(m)

m<-lmer(Degree ~ Should + ( Should | subID ) + (1 | identity), data=fullLong)
summary(m)

m<-lmer(Degree ~ Sim + ( Sim | subID ) + (1 | identity), data=fullLong)
summary(m)

m<-lmer(Degree ~ Proto + ( Proto | subID ) + (1 | identity), data=fullLong)
summary(m)

m<-lmer(Degree ~ A + ( A | subID ) + (1 | identity), data=fullLong)
summary(m)

m<-lmer(Degree ~ A*D + ( A + D | subID ) + (1 | identity), data=fullLong)
summary(m)

m<-lmer(Degree ~ MemUnc + ( MemUnc | subID ) + (1 | identity), data=fullLong)
summary(m)

m<-lmer(Degree ~ IdUnc + ( IdUnc | subID ) + (1 | identity), data=fullLong)
summary(m)
```



```{r}
library(lmerTest)
m<-lmer(Should ~ Degree*Time + ( Degree + Time | subID ) + (1 | identity), data=fullLong)
summary(m)

m<-lmer(Salient ~ Degree*Time + ( Degree + Time | subID ) + (1 | identity), data=fullLong)
summary(m)

m<-lmer(Ent ~ Degree*Time + ( Degree + Time | subID ) + (1 | identity), data=fullLong)
summary(m)

m<-lmer(Proto ~ Degree*Time + ( Degree + Time | subID ) + (1 | identity), data=fullLong)
summary(m)
ggpredict(m, c("Time","Degree")) %>% plot()

m<-lmer(Sim ~ Degree*Time + ( Degree + Time | subID ) + (1 | identity), data=fullLong)
summary(m)

m<-lmer(P ~ Degree*Time + ( Degree + Time | subID ) + (1 | identity), data=fullLong)
summary(m)

m<-lmer(Should ~ Degree*Time + ( Degree + Time | subID ) + (1 | identity), data=fullLong)
summary(m)
```

```{r}
m<-lmer(I ~ IdUnc*Time + ( IdUnc + Time | subID ) + (1 | identity), data=fullLong)
summary(m)

m<-lmer(I ~ MemUnc*Time + ( MemUnc + Time | subID ) + (1 | identity), data=fullLong)
summary(m)
ggpredict(m, c("Time","MemUnc")) %>% plot()
```

```{r}
m<-lmer(I ~ GExp * BExp + ( GExp + BExp | subID ) + (1 | identity), data=fullLong)
summary(m)
ggpredict(m, c("GExp","BExp")) %>% plot()

m<-lmer(I ~ Ent * Time +  ( Ent + Time | subID ) + (1 | identity), data=fullLong)
summary(m)
ggpredict(m, c("Time","Ent")) %>% plot()

m<-lmer(Degree ~ Ent * Time +  ( Ent + Time | subID ) + (1 | identity), data=fullLong)
summary(m)
ggpredict(m, c("Time","Ent")) %>% plot()

m<-lmer(I ~ Degree * Time +  ( Degree + Time | subID ) + (1 | identity), data=fullLong)
summary(m)
ggpredict(m, c("Time","Degree")) %>% plot()
```




## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
