---
title: "Longitudinal Modeling of Identity Relations and Experiences"
format: revealjs
editor: visual
---

```{r, echo=FALSE, include=FALSE}
library(groundhog)
pkgs <-  c("tidyverse","here", "lmerTest", "sjPlot","broom.mixed", "kableExtra", "ggeffects", "gt", "brms", "bayestestR")
groundhog.day <- '2022-07-25'
groundhog.library(pkgs, groundhog.day)
here::i_am("Analyses/idNetPrelimAnalyses.Rmd")
```

```{r, include=FALSE}
fullLong <- read.csv(here("Data/longIdentityNet.csv"))
fullShort <- read.csv(here("Data/shortIdentityNet.csv"))
fullData <- fullLong %>% full_join(fullShort, by = c("subID","Time"))
```

```{r,include=FALSE}
scaled <- apply(fullData[4:ncol(fullData)], 2, function(x) scale(x))
colnames(scaled) <- paste0(colnames(scaled),".Z")
fullData <- cbind(fullData, scaled)


scaled <- apply(fullShort[2:ncol(fullShort)], 2, function(x) scale(x))
colnames(scaled) <- paste0(colnames(scaled),".Z")
fullShort <- cbind(fullShort, scaled)

fullData <- fullData %>% mutate_at(c("Salient", "I", "M", "I", "P", "St", "Ent", "Sim", "Proto", "A", "D", "MemUnc", "IdUnc", "Should", "Consist", "Salient", "Ideal", "BExp", "GExp", "BelPer"), ordered)
```

```{r, include=FALSE}
ncores = parallel::detectCores()
options(mc.cores = parallel::detectCores())
```

# Background

## Self-Categorization

-   Self-Stereotyping: Evaluate self in terms of the group prototype, and apply ingroup norms and values onto the self (Hogg & Turner, 1987).

    -   If a group is accessible in terms of its compatibility with past experiences, present expectations, and current motives, values, goals and needs

    -   Comparison to out-group, such that I feel more similar to in- than out-group

    -   Fit the normative attributes of the group

## Motivations to identify with social groups

-   Stereotype Threat: Feeling at risk of fulfilling a stereotype thereby contributes to fulfilling the stereotype (Steele & Aranson, 1995).
-   Identity-Based Motivation Theory: People interpret experiences and situational difficulties in ways that are consistent with salient identity (Oyserman, 2010).

## Motivations to identify with social groups

-   Self-Uncertainty Theory: People will identify with groups to reduce self-uncertainty, particularly groups perceived as entitative (Hogg, 2007).
-   Optimal Distinctiveness Theory: People identify to maximize feelings of assimilation within groups and feelings of distinctiveness from other groups (Brewer, 1991).

## Multiple Identities

-   Self-complexity (Linville, 1987): a person's perceived knowledge of themself, based upon the number of distinct cognitive structures, or self-aspects, they believe to possess.
-   Self-structure (Showers, 1992): the way in which self-knowledge is organized
-   Social identity complexity (Roccas & Brewer, 2002): how individuals subjectively represent the relationships among their multiple ingroup memberships

## Multiple Identities

-   Self-concept map (Gresky, 2005): Draw a map from 'me' to self-definitional qualities
-   Multiple Self-Aspects Framework (McConnell, 2011) self-aspects are associated with personal attributes, which become more accessible when the self-aspect is activated and vice versa.
-   Social Identity Mapping Tool (Cruwys et al., 2011) is a a method for visually representing and assessing a person's subjective network of group memberships.

## Longitudinal Network Analysis

-   There have been some applications of longitudinal social network analysis

    -   Changes in friendships (Sijtsema et al., 2010)

    -   Bullying changes (Rambaran et al., 2020)

    -   Internalizing/externalizing changes (Fortuin et al., 2015)

-   Not yet applied to intrapersonal processes, such as identity relations

## Procedure

-   Participants recruited across 4 timepoints

-   Indicate open ended responses for up to 15 identities/groups they belong to

-   Indicate relations among each identity, and the amount of similarity between identities

-   Construct a weighted and unweighted graph where nodes remain static but relations change across timepoints

## Items

-   **Identification:** I identify as XXX.

-   **Positivity:** How positive do you feel about being a member of this group: XX

-   **Mutability:** It is easy to leave membership of this group: XX

-   **Entitativity:** XX is a cohesive, united, and tight-knit group.

-   **Group Similarity:** XX people are similar to each other.

-   **Self-Prototypicality:** I am representative and fit the description of what it means to be XX

## Items (continued)

-   **Stigma:** How stigmatized is XX ?

-   **Size:** To what extent do you feel your XX identity is small and not well-represented (i.e., minority) or large and well-represented (i.e., majority) at your university and in the United States?

-   **Assimilation:** I am included in the XX group and fit in/belong.

-   **Differentiation:** This group is distinct and different from other groups: XX

## Items (continued)

-   **Warmth:** Next we would like to get your feelings towards your XX identity and other XX groups using something we call the feeling thermometer that ranges from 0 to 100.
-   **Membership Uncertainty:** I feel uncertain that I will be accepted by others as typical/representative of being XX
-   **Identity Uncertainty:** I feel uncertain about the characteristics that define being XX

## Items (continued)

-   **Should:** How often do you feel that you [*should*]{.underline} engage in behaviors consistent with being XX? Consider how you generally think of yourself or others behaving, acting or feeling as a member of this group/identity.

-   **Consistent:** As of the past 1-2 weeks, I engaged in behaviors, thoughts, and feelings consistent with being XX. Consider how you generally think of yourself or others behaving, acting or feeling as a member of this group/identity.

## Items (continued)

-   **Salient:** As of the past 1-2 weeks, how often did you have salient or meaningful experiences related to being XX? Consider how you generally think of yourself or others behaving, acting or feeling as a member of this group/identity.

-   **Ideal:** How important is it to you to belong to this group: XX?

-   **Bad Experiences:** As of the past 1-2 weeks, how many threatening, stressful, or stigmatizing experiences have you had related to being XX?

## Items (continued)

-   **Good Experiences:** As of the past 1-2 weeks, how many positive and affirming experiences have you had related to being XX?

-   **Categorized:** As of the past 1-2 weeks, others perceive me as belonging to this group: XX.

## Hypotheses

-   While there are hypotheses, this study was general quite exploratory.

## Analysis Plan

-   Modeling Likert scale outcomes using Cumulative Link model

-   Evaluating magnitude and uncertainty of evidence using Bayesian modeling

-   Longitudinal multilevel models (i.e., growth models) with crossed random factors for participant and social identities, repeated across four timepoints

# Identification as a Function of Identity-Relevant Experiences

## Salient identity-relevant events predict greater social identification

```{r, echo=FALSE, warning=FALSE, include=FALSE}
m<-brm(I ~ Salient.Z + ( Salient.Z | subID) + (1 | identity), data=fullData, silent=2, refresh=0, cores=ncores, refresh=0, family = cumulative("probit"))

```

```{r, echo=FALSE}
sexit(m) %>% kbl() %>%
  kable_paper("hover", full_width = T, fixed_thead = T, font_size = 25)
cond<- conditional_effects(m)

ggplot(cond[[1]], aes(Salient.Z, estimate__)) + geom_smooth(method="lm") + geom_ribbon(aes(ymin=lower__, ymax=upper__), alpha=0.15) + xlab("Salience") + ylab("Identification")
```

## Positive Experiences Predict Greater Social Identification

```{r, echo=FALSE, warning=FALSE, include=FALSE}
m<-brm(I ~ GExp.Z + BExp.Z + ( GExp.Z + BExp.Z | subID ) + (1 | identity), data=fullData, silent=2, refresh=0, cores=ncores, refresh=0, family = cumulative("probit"))
```

```{r, echo = FALSE}
sexit(m) %>% kbl() %>%
  kable_paper("hover", full_width = T, fixed_thead = T, font_size = 25)
cond<- conditional_effects(m)

ggplot(cond[[1]], aes(GExp.Z, estimate__)) + geom_smooth(method="lm") + geom_ribbon(aes(ymin=lower__, ymax=upper__), alpha=0.15) + xlab("Good Experiences") + ylab("Identification")

ggplot(cond[[2]], aes(BExp.Z, estimate__)) + geom_smooth(method="lm") + geom_ribbon(aes(ymin=lower__, ymax=upper__), alpha=0.15) + xlab("Bad Experiences") + ylab("Identification")
```

## Feeling Prototypical Predicts Social Identification

```{r, echo=FALSE, warning=FALSE, include=FALSE}
m<-brm(I ~ Proto.Z * Time.Z + ( Proto.Z + Time.Z | subID ) + (1 | identity), data=fullData, silent=2, refresh=0, cores=ncores, refresh=0, family = cumulative("probit"))

```

```{r, echo=FALSE}
sexit(m) %>% kbl() %>%
  kable_paper("hover", full_width = T, fixed_thead = T, font_size = 25)
cond <- conditional_effects(m, effects = c("Proto.Z","Time.Z:Proto.Z"))

ggplot(cond[[1]], aes(effect1__, estimate__)) +  geom_line(method="lm") + geom_ribbon(aes(ymin=lower__, ymax=upper__), alpha=0.15) + xlab("Prototypicality") + ylab("Identification") + jtools::theme_apa()

ggplot(cond[[2]], aes(effect1__, estimate__)) +  geom_line(aes(linetype=as.factor(effect2__), color=as.factor(effect2__) )) + geom_ribbon(aes(ymin=lower__, ymax=upper__, fill=as.factor(effect2__) ), alpha=0.15) + xlab("Time") + ylab("Identification")  +
  labs(linetype="Prototypicality",color="Prototypicality",fill="Prototypicality") + jtools::theme_apa()
```

## Feeling assimilated predicts greater identification

```{r, echo=FALSE, warning=FALSE, include=FALSE}
m<-brm(I ~ A.Z * Time.Z + ( A.Z + Time.Z | subID ) + (1 | identity), data=fullData, silent=2, refresh=0, cores=ncores, refresh=0, family = cumulative("probit"))

```

```{r, echo = FALSE}
sexit(m) %>% kbl() %>%
  kable_paper("hover", full_width = T, fixed_thead = T, font_size = 25)
cond <- conditional_effects(m, effects = c("A.Z","Time.Z:A.Z"))

ggplot(cond[[1]], aes(effect1__, estimate__)) +  geom_line(method="lm") + geom_ribbon(aes(ymin=lower__, ymax=upper__), alpha=0.15) + xlab("Assimilation") + ylab("Identification") + jtools::theme_apa()

ggplot(cond[[2]], aes(effect1__, estimate__)) +  geom_line(aes(linetype=as.factor(effect2__), color=as.factor(effect2__) )) + geom_ribbon(aes(ymin=lower__, ymax=upper__, fill=as.factor(effect2__) ), alpha=0.15) + xlab("Time") + ylab("Identification")  +
  labs(linetype="Assimilation",color="Assimilation",fill="Assimilation") + jtools::theme_apa()
```

## More Positive and Less Bad Experiences Predict Feeling Perceived as Belonging to Group By Others

```{r, echo=FALSE, warning=FALSE, include=FALSE}
m<-brm(BelPer ~ GExp.Z * BExp.Z + ( GExp.Z + BExp.Z | subID ) + (1 | identity), data=fullData, silent=2, refresh=0, cores=ncores, refresh=0, family = cumulative("probit"))
```

```{r, echo=FALSE}
sexit(m) %>% kbl() %>%
  kable_paper("hover", full_width = T, fixed_thead = T, font_size = 25)
cond <- conditional_effects(m)
conditional_effects(m)
```

## Perceiving group members as similar predicts more identification

```{r, echo=FALSE, warning=FALSE, include=FALSE}
m<-brm(I ~ Sim.Z * Time.Z + ( Sim.Z + Time.Z | subID ) + (1 | identity), data=fullData, silent=2, refresh=0, cores=ncores, refresh=0, family = cumulative("probit"))
```

```{r, echo=FALSE}
sexit(m) %>% kbl() %>%
  kable_paper("hover", full_width = T, fixed_thead = T, font_size = 25)
cond <- conditional_effects(m, effects = c("Sim","Time.Z:Sim.Z"))

ggplot(cond[[1]], aes(effect1__, estimate__)) +  geom_line(method="lm") + geom_ribbon(aes(ymin=lower__, ymax=upper__), alpha=0.15) + xlab("Perceived Similarity") + ylab("Identification") + jtools::theme_apa()

ggplot(cond[[2]], aes(effect1__, estimate__)) +  geom_line(aes(linetype=as.factor(effect2__), color=as.factor(effect2__) )) + geom_ribbon(aes(ymin=lower__, ymax=upper__, fill=as.factor(effect2__) ), alpha=0.15) + xlab("Time") + ylab("Identification")  +
  labs(linetype="Perceived Similarity",color="Perceived Similarity",fill="Perceived Similarity") + jtools::theme_apa()
```

## Perceiving self as representative of group predicts more identification

```{r, echo=FALSE, warning=FALSE, include=FALSE}
m<-brm(I ~ Proto.Z * Time.Z + ( Proto.Z + Time.Z | subID ) + (1 | identity), data=fullData, silent=2, refresh=0, cores=ncores, refresh=0, family = cumulative("probit"))
```

```{r, echo=FALSE}
sexit(m) %>% kbl() %>%
  kable_paper("hover", full_width = T, fixed_thead = T, font_size = 25)
ggpredict(m, c("Time.Z","Proto.Z[1,4,7]")) %>% plot(show.title=F) + xlab("Time") + ylab("Identification") + jtools::theme_apa()
```

## Stigma Perception Predicts Greater Membership Uncertainty

```{r}
m<-lmer(MemUnc.Z ~ St.Z * Time.Z + ( St.Z + Time.Z | subID ) + ( St.Z + Time.Z | identity), data=fullData)
tidy(m,conf.int=TRUE,effects="fixed") %>% kbl() %>%
  kable_paper("hover", full_width = T, fixed_thead = T, font_size = 15)
ggpredict(m, c("Time.Z","St.Z[1,4,7]")) %>% plot(show.title=F) + xlab("Time") + ylab("Positivity of Connected Identities") + jtools::theme_apa()
```

# Propagation

## Spread of Positivity

As identity perceived more positively, it's neighboring connected identities are also perceived more positively

```{r}
m<-lmer(P_neigh ~ P * Time + ( P + Time | subID ) + (1 | identity), data=fullData)
tidy(m,conf.int=TRUE,effects="fixed") %>% kbl() %>%
  kable_paper("hover", full_width = T, fixed_thead = T, font_size = 25)
ggpredict(m, c("Time","P[1,4,7]")) %>% plot(show.title=F) + xlab("Time") + ylab("Positivity of Connected Identities") + jtools::theme_apa()
```

## Spread of Uncertainty About What It Means to be Identity

As people perceive more uncertainty about identity, it's neighboring connected identities are also perceived uncertainly.

```{r}
m<-lmer(IdUnc_neigh.Z ~ IdUnc.Z * Time.Z + ( IdUnc.Z | subID ) + ( Time.Z | identity), data=fullData)
tidy(m,conf.int=TRUE,effects="fixed") %>% kbl() %>%   kable_paper("hover", full_width = T, fixed_thead = T, font_size = 25)
tidy(m,conf.int=TRUE,effects="fixed") %>% kbl() %>%
  kable_paper("hover", full_width = T, fixed_thead = T, font_size = 25)
ggpredict(m, c("Time.Z","IdUnc.Z[-1.5,0,1.5]")) %>% plot(show.title=F) + xlab("Time") + ylab("Uncertainty About Neighboring Identities") + jtools::theme_apa()
```

## Spread of Self-Prototypicality

As people perceive themselves as more prototypical of a group, they also perceive themselves as more prototypical of connected groups

```{r}
m<-lmer(Proto_neigh.Z ~ Proto.Z * Time.Z + ( Proto.Z | subID ) + ( Time.Z | identity), data=fullData)
tidy(m,conf.int=TRUE,effects="fixed") %>% kbl() %>%   kable_paper("hover", full_width = T, fixed_thead = T, font_size = 25)
tidy(m,conf.int=TRUE,effects="fixed") %>% kbl() %>%
  kable_paper("hover", full_width = T, fixed_thead = T, font_size = 25)
ggpredict(m, c("Time.Z","Proto.Z[-1.5,0,1.5]")) %>% plot(show.title=F) + xlab("Time") + ylab("Self-Prototypicality of Neighboring Identities") + jtools::theme_apa()
```

## Spread of Group Similarity

As people perceive group members as more similar to one another, they also perceive members of connected groups as more similar to one another.

```{r}
m<-lmer(Sim_neigh.Z ~ Sim.Z * Time.Z + ( Sim.Z | subID ) + ( Time.Z | identity), data=fullData)
tidy(m,conf.int=TRUE,effects="fixed") %>% kbl() %>%   kable_paper("hover", full_width = T, fixed_thead = T, font_size = 25)
tidy(m,conf.int=TRUE,effects="fixed") %>% kbl() %>%
  kable_paper("hover", full_width = T, fixed_thead = T, font_size = 25)
ggpredict(m, c("Time.Z","Sim.Z[-1.5,0,1.5]")) %>% plot(show.title=F) + xlab("Time") + ylab("Self-Prototypicality of Neighboring Identities") + jtools::theme_apa()
```

## Spread of Identity-Obligation on Connected Identification

Main effect of feeling like you are obligated to behave like your identity on connected identities

```{r}
m<-lmer(I_neigh.Z ~ Should.Z * Time.Z + ( Should.Z | subID ) + ( Time.Z | identity), data=fullData)
tidy(m,conf.int=TRUE,effects="fixed") %>% kbl() %>%   kable_paper("hover", full_width = T, fixed_thead = T, font_size = 25)
tidy(m,conf.int=TRUE,effects="fixed") %>% kbl() %>%
  kable_paper("hover", full_width = T, fixed_thead = T, font_size = 25)
```

# Degree Centrality and Identity Strength

## Intergroup Bias

***Number of connections weakly predicts bias***

```{r}
m<-lmer(bias.Z ~  degree.Z * Time.Z + numID + ( degree.Z | subID ) + ( numID | identity), data=fullData)
tidy(m,conf.int=TRUE,effects="fixed") %>% kbl() %>%   kable_paper("hover", full_width = T, fixed_thead = T, font_size = 25)
```

***Strength of connections does not predict bias***

```{r}
m<-lmer(bias.Z ~  strength.Z + Time.Z + numID + ( strength.Z | subID ) + ( numID | identity), data=fullData)
tidy(m,conf.int=TRUE,effects="fixed") %>% kbl() %>%   kable_paper("hover", full_width = T, fixed_thead = T, font_size = 25)
```

***Modeling both simultaneously, number of connections weakly predicts bias***

```{r}
m<-lmer(bias.Z ~  strength.Z + degree.Z + Time.Z + numID + ( strength.Z | subID ) + ( numID | identity), data=fullData)
tidy(m,conf.int=TRUE,effects="fixed") %>% kbl() %>%   kable_paper("hover", full_width = T, fixed_thead = T, font_size = 25)
```

## Strength of identification

***Number of connections does not predict strength of identification***

```{r}
m<-lmer(I.Z ~ degree.Z + ( degree.Z | subID ) + ( degree.Z | identity), data=fullData)
tidy(m,conf.int=TRUE,effects="fixed") %>% kbl() %>%
  kable_paper("hover", full_width = T, fixed_thead = T, font_size = 25)
```

***But strength of connections [does]{.underline} predict strength of identification***

```{r}
m<-lmer(I.Z ~ strength.Z + ( strength.Z | subID ) + ( strength.Z | identity), data=fullData)
tidy(m,conf.int=TRUE,effects="fixed") %>% kbl() %>%
  kable_paper("hover", full_width = T, fixed_thead = T, font_size = 25)
```

## Ability to leave group membership (i.e., mutability)

***Number of connections marginally negatively predicts mutability***

```{r}
m<-lmer(M.Z ~ degree.Z + ( degree.Z | subID ) + ( degree.Z | identity), data=fullData)
tidy(m,conf.int=TRUE,effects="fixed") %>% kbl() %>%
  kable_paper("hover", full_width = T, fixed_thead = T, font_size = 25)
```

***Strength of connections more strongly negatively predicts mutability***

```{r}
m<-lmer(M.Z ~ strength.Z + ( strength.Z | subID ) + ( strength.Z | identity), data=fullData)
tidy(m,conf.int=TRUE,effects="fixed") %>% kbl() %>%
  kable_paper("hover", full_width = T, fixed_thead = T, font_size = 25)
```

## Positivity of group

***Number of connections [don't]{.underline} predict positivity***

```{r}
m<-lmer(P.Z ~ degree.Z + ( degree.Z | subID ) + ( degree.Z | identity), data=fullData)
tidy(m,conf.int=TRUE,effects="fixed") %>% kbl() %>%
  kable_paper("hover", full_width = T, fixed_thead = T, font_size = 25)
```

***Strength of connections [do]{.underline} more strongly negatively predicts positivity***

```{r}
m<-lmer(P.Z ~ strength.Z + ( strength.Z | subID ) + ( strength.Z | identity), data=fullData)
tidy(m,conf.int=TRUE,effects="fixed") %>% kbl() %>%
  kable_paper("hover", full_width = T, fixed_thead = T, font_size = 25)
```

## Self-prototypicality

***Number of connections [don't]{.underline} predict self-prototypicality***

```{r}
m<-lmer(Proto.Z ~ degree.Z + ( degree.Z | subID ) + ( degree.Z | identity), data=fullData)
tidy(m,conf.int=TRUE,effects="fixed") %>% kbl() %>%
  kable_paper("hover", full_width = T, fixed_thead = T, font_size = 25)
```

***Strength of connections [do]{.underline} more strongly predicts self-prototypicality***

```{r}
m<-lmer(Proto.Z ~ strength.Z + ( strength.Z | subID ) + ( strength.Z | identity), data=fullData)
tidy(m,conf.int=TRUE,effects="fixed") %>% kbl() %>%
  kable_paper("hover", full_width = T, fixed_thead = T, font_size = 25)
```

# Individual Differences

## Individual Differences in Bias

------------------------------------------------------------------------

### Need for Cognition

```{r}
m<-lmer(bias.Z ~ strength.Z * Time.Z + ( strength.Z | subID ) + ( 1 | identity), data=fullData)
tidy(m,conf.int=TRUE,effects="fixed") %>% kbl() %>%
  kable_paper("hover", full_width = T, fixed_thead = T, font_size = 25)
```

------------------------------------------------------------------------

### Self-Concept Clarity

```{r}
m<-lmer(I.Z ~ Time.Z * SCC.Z + ( Time.Z | subID ) + ( SCC.Z | identity), data=fullData)
tidy(m,conf.int=TRUE,effects="fixed") %>% kbl() %>%
  kable_paper("hover", full_width = T, fixed_thead = T, font_size = 25)
```

------------------------------------------------------------------------

### Self-Esteem

```{r}
m<-lmer(I.Z ~ Time.Z * SE.Z + ( Time.Z | subID ) + ( SE.Z | identity), data=fullData)
tidy(m,conf.int=TRUE,effects="fixed") %>% kbl() %>%
  kable_paper("hover", full_width = T, fixed_thead = T, font_size = 25)
```

## Individual Differences in Changes in Identification

------------------------------------------------------------------------

### Need for Cognition

```{r}
m<-lmer(I.Z ~ Time.Z * NFC.Z + ( Time.Z | subID ) + ( NFC.Z | identity), data=fullData)
tidy(m,conf.int=TRUE,effects="fixed") %>% kbl() %>%
  kable_paper("hover", full_width = T, fixed_thead = T, font_size = 25)
```

------------------------------------------------------------------------

### Self-Concept Clarity

```{r}
m<-lmer(I.Z ~ Time.Z * SCC.Z + ( Time.Z | subID ) + ( SCC.Z | identity), data=fullData)
tidy(m,conf.int=TRUE,effects="fixed") %>% kbl() %>%
  kable_paper("hover", full_width = T, fixed_thead = T, font_size = 25)
```

------------------------------------------------------------------------

### Self-Esteem

```{r}
m<-lmer(I.Z ~ Time.Z * SE.Z + ( Time.Z | subID ) + ( SE.Z | identity), data=fullData)
tidy(m,conf.int=TRUE,effects="fixed") %>% kbl() %>%
  kable_paper("hover", full_width = T, fixed_thead = T, font_size = 25)
```

## Individual Differences in Changes in Mutability

------------------------------------------------------------------------

### Need for Cognition

```{r}
m<-lmer(M.Z ~ Time.Z * NFC.Z + ( Time.Z | subID ) + ( NFC.Z | identity), data=fullData)
tidy(m,conf.int=TRUE,effects="fixed") %>% kbl() %>%
  kable_paper("hover", full_width = T, fixed_thead = T, font_size = 25)
```

------------------------------------------------------------------------

### Self-Concept Clarity

```{r}
m<-lmer(M.Z ~ Time.Z * SCC.Z + ( Time.Z | subID ) + ( SCC.Z | identity), data=fullData)
tidy(m,conf.int=TRUE,effects="fixed") %>% kbl() %>%
  kable_paper("hover", full_width = T, fixed_thead = T, font_size = 25)
```

------------------------------------------------------------------------

### Self-Esteem

```{r}
m<-lmer(M.Z ~ Time.Z * SE.Z + ( Time.Z | subID ) + ( SE.Z | identity), data=fullData)
tidy(m,conf.int=TRUE,effects="fixed") %>% kbl() %>%
  kable_paper("hover", full_width = T, fixed_thead = T, font_size = 25)
```

## Individual Differences in the Effect of Obligation on Identification

------------------------------------------------------------------------

### Need for Cognition

```{r}
m<-lmer(I.Z ~ Should.Z * NFC.Z + ( Should.Z | subID ) + ( NFC.Z | identity), data=fullData)
tidy(m,conf.int=TRUE,effects="fixed") %>% kbl() %>%
  kable_paper("hover", full_width = T, fixed_thead = T, font_size = 25)
ggpredict(m, c("NFC.Z","Should.Z[-1,0,1]")) %>% plot(show.title=F) + xlab("Need for Cognition") + ylab("Identification") + jtools::theme_apa()
```

------------------------------------------------------------------------

### Self-Concept Clarity

At lower levels of self-concept clarity, feeling like you should behave like your group predicts more identification.

```{r}
m<-lmer(I.Z ~ Should.Z * SCC.Z + ( Should.Z | subID ) + ( SCC.Z | identity), data=fullData)
tidy(m,conf.int=TRUE,effects="fixed") %>% kbl() %>%
  kable_paper("hover", full_width = T, fixed_thead = T, font_size = 25)
ggpredict(m, c("SCC.Z","Should.Z[-1,0,1]")) %>% plot(show.title=F) + xlab("Self-Concept Clarity") + ylab("Identification") + jtools::theme_apa()
```

------------------------------------------------------------------------

### Self-Esteem

```{r}
m<-lmer(I.Z ~ Should.Z * SE.Z + ( Should.Z | subID ) + ( SE.Z | identity), data=fullData)
tidy(m,conf.int=TRUE,effects="fixed") %>% kbl() %>%
  kable_paper("hover", full_width = T, fixed_thead = T, font_size = 25)
ggpredict(m, c("SE.Z","Should.Z[-1,0,1]")) %>% plot(show.title=F) + xlab("Self-Esteem") + ylab("Identification") + jtools::theme_apa()
```

## Individual Differences in the Effect of Salience on Identification

------------------------------------------------------------------------

### Need for Cognition

```{r}
m<-lmer(I.Z ~ Salient.Z * NFC.Z + ( Salient.Z | subID ) + ( NFC.Z | identity), data=fullData)
tidy(m,conf.int=TRUE,effects="fixed") %>% kbl() %>%
  kable_paper("hover", full_width = T, fixed_thead = T, font_size = 25)
ggpredict(m, c("NFC.Z","Salient.Z[-1,0,1]")) %>% plot(show.title=F) + xlab("Need for Cognition") + ylab("Identification") + jtools::theme_apa()
```

------------------------------------------------------------------------

### Self-Concept Clarity

```{r}
m<-lmer(I.Z ~ Salient.Z * SCC.Z + ( Salient.Z | subID ) + ( SCC.Z | identity), data=fullData)
tidy(m,conf.int=TRUE,effects="fixed") %>% kbl() %>%
  kable_paper("hover", full_width = T, fixed_thead = T, font_size = 25)
ggpredict(m, c("SCC.Z","Salient.Z[-1,0,1]")) %>% plot(show.title=F) + xlab("Self-Concept Clarity") + ylab("Identification") + jtools::theme_apa()
```

------------------------------------------------------------------------

### Self-Esteem

```{r}
m<-lmer(I.Z ~ Salient.Z * SE.Z + ( Salient.Z | subID ) + ( SE.Z | identity), data=fullData)
tidy(m,conf.int=TRUE,effects="fixed") %>% kbl() %>%
  kable_paper("hover", full_width = T, fixed_thead = T, font_size = 25)
ggpredict(m, c("SE.Z","Should.Z[-1,0,1]")) %>% plot(show.title=F) + xlab("Self-Esteem") + ylab("Identification") + jtools::theme_apa()
```

## Individual Differences in the Effect of Stigma on Identification

------------------------------------------------------------------------

### Need for Cognition

```{r}
m<-lmer(I.Z ~ St.Z * NFC.Z + ( St.Z | subID ) + ( NFC.Z | identity), data=fullData)
tidy(m,conf.int=TRUE,effects="fixed") %>% kbl() %>%
  kable_paper("hover", full_width = T, fixed_thead = T, font_size = 25)
ggpredict(m, c("NFC.Z","St.Z[-1,0,1]")) %>% plot(show.title=F) + xlab("Need for Cognition") + ylab("Identification") + jtools::theme_apa()
```

------------------------------------------------------------------------

### Self-Concept Clarity

```{r}
m<-lmer(I.Z ~ St.Z * SCC.Z + ( St.Z | subID ) + ( SCC.Z | identity), data=fullData)
tidy(m,conf.int=TRUE,effects="fixed") %>% kbl() %>%
  kable_paper("hover", full_width = T, fixed_thead = T, font_size = 25)
ggpredict(m, c("SCC.Z","St.Z[-1,0,1]")) %>% plot(show.title=F) + xlab("Self-Concept Clarity") + ylab("Identification") + jtools::theme_apa()
```

------------------------------------------------------------------------

### Self-Esteem

```{r}
m<-lmer(I.Z ~ St.Z * SE.Z + ( St.Z | subID ) + ( SE.Z | identity), data=fullData)
tidy(m,conf.int=TRUE,effects="fixed") %>% kbl() %>%
  kable_paper("hover", full_width = T, fixed_thead = T, font_size = 25)
ggpredict(m, c("SE.Z","St.Z[-1,0,1]")) %>% plot(show.title=F) + xlab("Self-Esteem") + ylab("Identification") + jtools::theme_apa()
```

## Individual Differences in the Effect of Good and Bad Experiences on Identification

------------------------------------------------------------------------

### Need for Cognition

```{r}
m<-lmer(I.Z ~ GExp.Z * NFC.Z + BExp.Z * NFC.Z + ( BExp.Z + GExp.Z | subID ) + ( NFC.Z | identity), data=fullData)
tidy(m,conf.int=TRUE,effects="fixed") %>% kbl() %>%
  kable_paper("hover", full_width = T, fixed_thead = T, font_size = 25)
```

------------------------------------------------------------------------

### Self-Concept Clarity

```{r}
m<-lmer(I.Z ~ GExp.Z * SCC.Z + BExp.Z * SCC.Z + ( BExp.Z + GExp.Z | subID ) + ( SCC.Z | identity), data=fullData)
tidy(m,conf.int=TRUE,effects="fixed") %>% kbl() %>%
  kable_paper("hover", full_width = T, fixed_thead = T, font_size = 25)
```

------------------------------------------------------------------------

### Self-Esteem

```{r}
m<-lmer(I.Z ~ GExp.Z * SE.Z + BExp.Z * SE.Z + ( BExp.Z + GExp.Z | subID ) + ( SE.Z | identity), data=fullData)
tidy(m,conf.int=TRUE,effects="fixed") %>% kbl() %>%
  kable_paper("hover", full_width = T, fixed_thead = T, font_size = 25)
```

## Individual Differences in Identity Strength

------------------------------------------------------------------------

### Need for Cognition

```{r}
m <- lmer(sumStre.Z~NFC.Z * Time.Z 
                 + ( Time.Z |subID),
                 data=fullShort)
tidy(m,conf.int=TRUE,effects="fixed") %>% kbl() %>%   kable_paper("hover", full_width = T, fixed_thead = T, font_size = 25)
```

------------------------------------------------------------------------

### Self-Esteem

```{r}
m <- lmer(sumStre.Z~SE.Z * Time.Z 
                 + ( Time.Z |subID),
                 data=fullShort)
tidy(m,conf.int=TRUE,effects="fixed") %>% kbl() %>%   kable_paper("hover", full_width = T, fixed_thead = T, font_size = 25)
```

------------------------------------------------------------------------

### Self-Concept Clarity

```{r}
m <- lmer(sumStre.Z~SCC.Z * Time.Z 
                 + ( Time.Z |subID),
                 data=fullShort)
tidy(m,conf.int=TRUE,effects="fixed") %>% kbl() %>%   kable_paper("hover", full_width = T, fixed_thead = T, font_size = 25)
```

## Individual Differences in Number of Identities

------------------------------------------------------------------------

### Need for Cognition

```{r}
m <- glmer(numID~NFC.Z * Time.Z 
                 + ( Time.Z |subID),
                 data=fullShort, family="poisson")
tidy(m,conf.int=TRUE,effects="fixed") %>% kbl() %>%   kable_paper("hover", full_width = T, fixed_thead = T, font_size = 25)
```

------------------------------------------------------------------------

### Self-Esteem

```{r}
m <- glmer(numID~SE.Z * Time.Z 
                 + ( Time.Z |subID),
                 data=fullShort, family="poisson")
tidy(m,conf.int=TRUE,effects="fixed") %>% kbl() %>%   kable_paper("hover", full_width = T, fixed_thead = T, font_size = 25)
```

------------------------------------------------------------------------

### Self-Concept Clarity

```{r}
m <- glmer(numID~SCC.Z * Time.Z 
                 + ( Time.Z |subID),
                 data=fullShort, family="poisson")
tidy(m,conf.int=TRUE,effects="fixed") %>% kbl() %>%   kable_paper("hover", full_width = T, fixed_thead = T, font_size = 25)
```

## Individual Differences in Network Density

------------------------------------------------------------------------

### Need for Cognition

```{r}
m <- lmer(dense.Z~NFC.Z * Time.Z 
                 + ( Time.Z |subID),
                 data=fullShort)
tidy(m,conf.int=TRUE,effects="fixed") %>% kbl() %>%   kable_paper("hover", full_width = T, fixed_thead = T, font_size = 25)
```

------------------------------------------------------------------------

### Self-Esteem

```{r}
m <- lmer(dense.Z~SE.Z * Time.Z 
                 + ( Time.Z |subID),
                 data=fullShort)
tidy(m,conf.int=TRUE,effects="fixed") %>% kbl() %>%   kable_paper("hover", full_width = T, fixed_thead = T, font_size = 25)
```

------------------------------------------------------------------------

### Self-Concept Clarity

Higher self-concept clarity predicts less density across time and lower self-concept clarity predicts more density across time

```{r}
m <- lmer(dense.Z~SCC.Z * Time.Z 
                 + ( Time.Z |subID),
                 data=fullShort)
tidy(m,conf.int=TRUE,effects="fixed") %>% kbl() %>%   kable_paper("hover", full_width = T, fixed_thead = T, font_size = 25)
ggpredict(m, c("Time.Z","SCC.Z")) %>% plot(show.title=F) + xlab("Time") + ylab("Identity Network Density") + jtools::theme_apa()
```

## Individual Differences in Network Density

------------------------------------------------------------------------

### Need for Cognition

```{r}
m <- lmer(dense.Z~NFC.Z * Time.Z 
                 + ( Time.Z |subID),
                 data=fullShort)
tidy(m,conf.int=TRUE,effects="fixed") %>% kbl() %>%   kable_paper("hover", full_width = T, fixed_thead = T, font_size = 25)
```

------------------------------------------------------------------------

### Self-Esteem

```{r}
m <- lmer(dense.Z~SE.Z * Time.Z 
                 + ( Time.Z |subID),
                 data=fullShort)
tidy(m,conf.int=TRUE,effects="fixed") %>% kbl() %>%   kable_paper("hover", full_width = T, fixed_thead = T, font_size = 25)
```

------------------------------------------------------------------------

### Self-Concept Clarity

```{r}
m <- lmer(dense.Z~SCC.Z * Time.Z 
                 + ( Time.Z |subID),
                 data=fullShort)
tidy(m,conf.int=TRUE,effects="fixed") %>% kbl() %>%   kable_paper("hover", full_width = T, fixed_thead = T, font_size = 25)
ggpredict(m, c("Time.Z","SCC.Z")) %>% plot(show.title=F) + xlab("Time") + ylab("Identity Network Density") + jtools::theme_apa()
```

## Does social identity complexity (i.e., summed similarity) relate to intergroup bias?

------------------------------------------------------------------------

### Summed Similarity

```{r}
m <- lmer(idSimGlob.Z~totalBias.Z * Time.Z + varBias.Z + 
                 + ( Time.Z |subID),
                 data=fullShort)
tidy(m,conf.int=TRUE,effects="fixed") %>% kbl() %>%   kable_paper("hover", full_width = T, fixed_thead = T, font_size = 25)
ggpredict(m, c("Time.Z","totalBias.Z")) %>% plot(show.title=F) + xlab("Time") + ylab("Intergroup Bias") + jtools::theme_apa()
```

------------------------------------------------------------------------

### Mean Strength

```{r}
m <- lmer(meanStre.Z~totalBias.Z + Time.Z + varBias.Z + numID +
                 + ( Time.Z |subID),
                 data=fullShort)
tidy(m,conf.int=TRUE,effects="fixed") %>% kbl() %>%   kable_paper("hover", full_width = T, fixed_thead = T, font_size = 25)

```

# Questions/Comments?
